### 2024-03-13 Scripts/Manuscript/manuscript.Rmd
finished appendices, and adjusted introductionb, methods. and results sections.

However, many researchers have also raised concerns that other factors, such as low power [@stanley2018what], lack of strong theoretical foundations [@eronen2021theory], and validity [@finkel2017replicability], which have not been given as much attention, are just as if not more responsible for the lack of successful replications found in psychology. An idea which has gained more traction recently is that measurement related issues have a large problematic influence on replicability. In particular, studies have focused on the effects of issues such as measurement error and questionable measurement practices on replicability [@stanley2014expectations; @shaw2020measurement; @flake2017construct; @flake2020measurement].

Measurement in psychological science is defined in large part by one overarching issue: psychological constructs, such as affective state and intelligence, cannot be measured directly. As a result, psychologists face two primary challenges in the use of measurement: First of all, the measure has to assess the construct it intends to measure, even though it can only do so indirectly. Secondly, because the measurement is indirect, it also comes with some degree of error surrounding its assessment of the construct. The first issue relates to the concept of validity, and specifically construct validity. Validity refers to the overall extent to which a measure measures what it is supposed to [@borsboom2004concept], while construct validity specifically refers to the substantial relation between the item scores on a psychological measure and the psychological construct it intends to measure. In order for indirect assessment of psychological constructs to be a viable approach, the measure needs to have construct validity [@cook2002experimental]. The second issue relates to the concept of measurement error and reliability. Measurement error indicates the amount of variation in item scores that is the result of the used measures inaccuracies, and not due to differences in the underlying psychological construct of interest.

@stanley2014expectations demonstrated, using a simulation study, the impact measurement error has on attempts to verify or falsify findings. Scalar item data was generated based on levels of sampling error and score-reliability, as the inverse of measurement error, that mimicked what is standard in psychological research, to ensure that the resulting degree of error was representative. The results indicated that measurement error caused observed effects found in replication research to vary heavily. ???relation measurement error and replicability (As a result, interpretations of replications might not be based on tests of the true effect, if the impact of measurement error is not attenuated for.)???

Another key aspect in evaluating the use of measures is how they are reported. Questionable Measurement Practices (QMPs) have been coined as a conjugate term to QRPs. QMPs are practices that decrease the information necessary to evaluate the measurement of a study. They range from lack of transparency and unclear motivation in choice of measure, to poor justification for modifications of measure and procedure of any sourced measures [@flake2020measurement]. When this information is missing, it becomes difficult to establish that original and replication are measuring the same construct(s), which has detrimental consequences for direct replication attempts.

This study aims to investigate the influence of measurement error and QMPs on replicability, using data and reports from the large scale Many Labs replication projects. One goal is to expand the research by [@stanley2014expectations] with a practical example. Whereas they obtained their findings using a simulation study, this study investigated the scope of their findings in practice. QMPs in the context of replication research were already investigated by [@flake2022construct]. However, the investigations remained mostly descriptive. This study aims to expand upon the findings of [@flake2022construct] through the use of a new set of replication data, and by investigating the relation between QMP and replicability.

@@

As a first step it is worth investigating what the state of measurement error is in original and replication research in psychology, in order to assess the scope of @stanley2014expectations's findings in practice. Thus, this study investigated the following:

@@

Since direct replications intend to investigate effects in nearly identical scenarios with nearly identical measures as the original study, it is expected that measurement errors are as present in replication research as in original psychological research.

@@

While reliability estimates are generally considered a measure specific feature, this is false. They are context dependent, and as a result the estimates of an effect can differ across contexts [@cho2015cronbach; @pauly2018resampling]. With large enough differences across contexts, the effect estimates between different replication attempts could deviate from each other beyond direct comparison. ???RELIABILITY VARIANCE IN META ANALYSIS???. To investigate this potential problem, the variation in score reliability is assessed for each measure when used in different contexts.

@@

Even though reliability estimates are context dependent, sufficient protocol structure can counteract the variance in reliability estimates. An example of the standardising impact a structured protocol can have on reducing variability within an effect can be found in investigations into the closely related issue of heterogeneity [@patacchini2007unobserved]. Heterogeneity refers to the true variation in the true effect size due to minor but key differences in context, environment, and procedure. Heterogeneity is yet another proposed explanation for failed replications. This concern even prompted a Many Labs centred around the testing of heterogeneity in replications [@klein2018many]. However analyses from Many Labs 2, and @olsson2020heterogeneity showed little empirical evidence for widespread heterogeneity in effects among replications. These findings demonstrate that it is possible to reduce variability as the result of context using structured protocols, as was done in the Many Labs projects this study analyzed.

@@

This study investigated whether there is something in the measures used for replicated findings that sets them apart from those used for non-replicated findings. In particular, this study extends research by @stanley2014expectations on the relationship between reliability and replicability, by using data from real life replication projects.

@@

Validity of measures can be assessed not only through features found in the data. The measure must also be chosen and implemented in a way that enables proper measurement of the variables [@flake2020measurement]. Any scientific report should therefore clearly motivate the measure and procedure that was used. Without clear reporting on these aspects, the validity of measurement will remain uncertain. Therefore, the other tests of this paper focused on the reporting aspects of measurement, assessed through QMPs.

This study seeks to conceptually replicate some of the findings of @flake2022construct about QMP reporting in the RPP within the Many Labs replication projects.

@@

QMPs may obscure relevant information needed to evaluate the use of measurement in a study. If the replication used the measure differently from the original, the replication may no longer be a direct replication. ???link not direct replication to lack of replication through larger variance argument??? For these reasons, establishing a link between QMPs and non-replicability should confirm suspicions of their detrimental effects on replications [@flake2017construct; @flake2020measurement; @flake2022construct].

@@

The total number of psychological findings for which replication was attempted across the four included Many Labs projects amounts to a total of 60. Each finding was tested across several labs, and was related to a finding from an original study, the combination of all these studies and their associated information formed a replication set. For each research finding, any primary measures assessing a unique variable were taken to form the key unit of analysis. Here primary measures refers to measures assessing variables included in the primary test of the replication. This was done to ensure that the analyses could link directly to the replicability of a study. Acquiescence bias checks, manipulation checks, measures used for pilot testing, and measures added for exploratory analyses in replication studies were not included.. The result was a total sample size of 77 measures. The Table BELOW show descriptive information about the data for each Many Labs Project.

DESCRIPTIVE TABLE

(Row 1: Many Labs projects - 13 in Many Labs 1; 28 in Many Labs 2; 10 in Many Labs 3; & finally 9 out of the 10 tested findings in Many Labs 5)

(Row 2: Primary measures - 14 in Many Labs 1; 35 in Many Labs 2; 15 in Many Labs 3; & 13 in Many Labs 5)

(Row 3: ???)

Footnote about sample size differences between original and original shortened.

@@

The data on the preregistered replication protocols, and replication datasets from Many Labs 1, 2, 3, & 5 were all retrieved from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>. Both the replication protocols and replication datasets were scanned through to ensure that the planned analyses were feasible. However, no coding or analysis of either of them had taken place before the analyses were preregistered. When available, codebooks and study materials were used to identify the specific data for each measure.

@@

The replication datasets refer to the data of each of the replication attempts for each of the original psychological effects undertaken as part of a Many Labs study. These publicly available datasets of the replication attempt were accessed through their OSF page and loaded into Rstudio [@R-Rstudio]. Using the replication protocols, codebooks, and analysis scripts from each replication set as a guide, the variables associated with each relevant measure were extracted into their own data frame containing the data from all studies in one replication set. These pieces of information were used as the datasets for their respective analyses.

The measure had to consist of multiple scalar items to be considered relevant, as single item measures were not usable for the planned analyses on score reliability [@wanous1996estimating], which followed up on @stanley2014expectations simulation study. If cleaned data was available this was chosen over raw data, to ensure that variables were coded as intended. Pilot data were omitted from the analyses entirely. These criterion resulted in suitable measure data from eighteen replication sets spread across on average 40 lab locations for the analyses of hypotheses 2 & 3.

DESCRIPTIVE TABLE???

@@

MAKE ALL FOOTNOTE?: (in reference to ML 5 mostly) The relevant OSF page of each replication set was searched through for a file which contained protocol in its name. If available, a version of the protocol labelled as revised, post-review, peer-review, or endorsed was selected. In case there was doubt about which was most appropriate, the latest uploaded relevant protocol was selected. Only regular protocols were taken, meaning those not labelled as data collection, analysis protocol or anything similar[^1].

[^1]: The steps taken to access the replication protocol data from Many Labs 5 were not preregistered, and only became clear upon further investigation of the accessible information. The specific names and locations of the files that were used as the datasets can be found under the supplementary materials of the OSF page of this article <https://osf.io/gft46/%7D>

@@

FOOTNOTE: The original articles were identified through the citations in each replication protocol, using Web of Science, Google Scholar, and PsychInfo (in that order). An issue was encountered while trying to access @hyman1950current. However, after contacting the first author of @klein2014investigating a suitable version of the article was obtained for use in the analyses.

@@

MOVE TO APPENDIX/COMBINE WITH EXTERNAL SEARCH STRATEGY FILE: The scope of the coding was limited to the abstract, method, procedure, materials, measure, and initial parts of the results sections. Additionally, a keyword search using the name of the measured variable was used to search for any potentially missed information. An exception to this procedure was a question asking about the presence of example items. For this question, information from supplementary materials was uniquely considered as relevant. Another exception was the question regarding the replication of the original effect. Tables from the final report of each Many Labs project were used to answer that question.

MOVE TO APPENDIX/COMBINE WITH EXTERNAL SEARCH STRATEGY FILE: These changes (to the QMP coding protocol) included: accepting linked online appendices as a data source for example items; assuming that if no differences between replication and original are measurement is mentioned, that there is no difference, even if it is not explicitly clear; and generally simplified criteria for what constituted sufficiently clear reporting.

@@

In order to answer questions regarding reported reliability, the reported reliability coefficient were extracted from both the replication protocols and the original articles. The reported reliability coefficient is the score reliability reported per measure in the replication protocol or original article. Both the type (Cronbach's alpha, retest, interrater, etc.) and the value itself were extracted.

@@

Cronbach's alpha was calculated as the main score reliability index used in the analyses as it is one of the most popular [@cho2015cronbach]. Analyses based on the Omega can be found in Appendix ???. Omega was included since it has been argued to be a more informative measure of score reliability, while also providing validity evidence for the scale [@crutzen2017scale; @deng2017testing]. Cronbach's alpha and omega were calculated using the alpha and omega functions respectively in the psych R package [@R-psych]. Default arguments were used for both functions except the nfactors in the omega function, which was set to 1.

@@

The tests for hypotheses 4, 5, & 6 were all based on the number of QMPs coded across both original articles and replication protocols. QMPs were all coded to be either true, false, or not applicable. Questions related to modification had 'no modification' as an additional answer option, in case the specific aspect of the measure was explicitly not modified. Each coded QMP belonged to one of five QMP type categories that were derived from the classification in @flake2020measurement. An overview of the QMP categories of the coding variables can be seen in Table \@ref(tab:QMPCodingInfoTable).

@@

For the analyses of these variables both the total QMP ratios and ratios per QMP type category were used. This ratio was based on the number of coded trues divided by the total number of applicable QMPs. QMPs were considered applicable if not coded as not applicable or no modification. These ratios were preferred over counts, since non applicable items could thus be accounted for. Formula \@ref(eq:QMPRatioType) shows the formula that was used to calculate the QMP ratio for a particular QMP type j, where True is 1 if that item was coded as True and 0 otherwise, and False is 1 if that item was coded as False and 0 otherwise, $j \subset \{ definition, operationalisation, selection/creation, quanitification, modification \}$, and $i = 1,..., n_{j-items}$.

FORMULA of QMP ratio:

```{=tex}
\begin{equation}
QMP_ratio_{j} = \frac{\sum_{n=1}^i True_{ij}}{\sum_{n=1}^i True_{ij} + False_{ij}} (\#eq:QMPRatioType)
\end{equation}
```
For the total QMP ratio:

```{=tex}
\begin{equation}
QMP_ratio = \frac{\sum_{n=1}^j \sum_{n=1}^i True_{ij}}{\sum_{n=1}^j \sum_{n=1}^i True_{ij} + False_{ij}} (\#eq:QMPRatioTotal)
\end{equation}
```
Eleven out of twenty of the QMP variables used to calculate the QMP ratio have an equivalent in the coding key of @flake2022construct. The remaining nine were either altered from the coding key to better fit the QMP counting operationalization, all newly created or modified items were based on the definitions of the QMP categories and their criteria as specified in @flake2020measurement. Beside these quantitative variables, a total of four qualitative variables were also included to provide more detailed information on some aspects of the measure and its reporting. Details on the items used, their origin and justifications can be seen in Supplementary Materials ???.

FOOTNOTE: additional analyses, tables and figures based on QMPs obtained with the initial protocol can be found in Appendix ???.

???Supplementary Materials: on item revision and origin

Two of the qualitative items have an equivalent in the coding key of Variables related to the specific measurement scaling and purpose in the paper, were omitted from the analyses of this study as they were deemed neither relevant for the analyses of this study, nor necessary in matching this study to the key results of @flake2022construct. Questions about more general measurement features such as the number of items and how scores were aggregated were altered from @flake2022construct to better fit the use of QMP ratios and associations between them and other coded aspects.

These (qualitative) variables assessed with two having an equivalent in @flake2022construct: the specific version of the measure (if reported); whether and what previous materials were used for the study; what, if any, psychometric evidence beyond reliability score (e.g. factor analysis, IRT model, convergent validity) was provided; and whether it was specified or not that the measure was or was not modified.???

After the data was initially coded according to the preregistered coding protocol, it was determined, based on discussion with the supervisor, that some of the initial ratings were possibly to stringent. As a result, some of the items in the protocol were reformulated, so that the conclusions from the resulting analyses were based on a more lenient judgement of QMPs. The revision of the coding protocol happened after all the data were coded using the initial protocol. As a result the coded data using the initial protocol, and the coded data using the revised protocol are both available available on this article's OSF (<https://osf.io/9r8yt/>) and github (<https://github.com/CasGoos/measurement_and_replication.git>) pages.

@@

Every hypothesis test in this study used an alpha significance cutoff of .05. No correction for multiple testing was applied, to ensure that the rate of false negatives remained low, the increase in false positive rate was accepted as they deemed less harmful to the exploratory aims of this study. This exploratory focus combined with the generally small sample size and consequently low power of the analyses in this article means that descriptives will be used to facilitate the interpretation of the results.

@@

The original test for hypothesis 1, a t-test of the reported Cronbach's alpha coefficient values between original and replication, could not be conducted, since not enough score reliabilities were reported to conduct the test and expect sensible results. Instead, the total number of reported reliability coefficients were compared between the replication protocols and the original articles. This comparison was tested via a chi-square test using the base R stats package [@R-base].

@@

While reported reliabilities were rare, some reliabilities could still be calculated from the replication datasets. On top of that, reliabilities could be calculated for each individual lab per replication set so that the variance of them could be assessed. In order to separate between and within variance in reliability, a multilevel random intercept model was specified with replication set as the grouping variable and the Cronbach's alpha or omega value of a replication as dependent using the lmer function from the lme4 package [@R-lme4] t. The formulas for this model, where $alpha_{ij}$ represents the calculated Cronbach's alpha coefficient of a single study at one lab location with $i = 1,..., n_{locations}$ and $j = 1,...,n_{replicationsets}$ look as follows:

@@

# and same analyses for omega
# intercept only model to check the within and between group variance.
H2_test_result_omega <- lmer(formula = omega ~ 1 + (1|g), data = data_h2[complete.cases(data_h2),])

@@

```{r ICCCalculations, include = FALSE}
# alpha
within_group_variance_alpha <- attr(VarCorr(H2_test_result_alpha), "sc")^2
between_group_variance_alpha <- attr(VarCorr(H2_test_result_alpha)$g, "stddev")^2

ICC_alpha <- between_group_variance_alpha / (within_group_variance_alpha + between_group_variance_alpha)

# omega
within_group_variance_omega <- attr(VarCorr(H2_test_result_omega), "sc")^2
between_group_variance_omega <- attr(VarCorr(H2_test_result_omega)$g, "stddev")^2

ICC_omega <- between_group_variance_omega / (within_group_variance_omega + between_group_variance_omega)

@@

???Other analyses were considered after [meta-analyses in particular]???

One of the key tests was that of hypothesis 3 relating to the association between reliability and replicability that had been indicated by @stanley2014expectations. The logistic regression shown in equation \@ref(eq:H3Main) was used to model this association, where $f(.)$ represents the logit link function, $i = 1,..., n_{replications}$, the outcome $replicated$ which was coded as 1 if the meta-analytic effect in the replication set matches the original effect in direction at a significance alpha level of .05, and 0 otherwise, and the predictor $alpha$ referred to the averaged calculated Cronbach's alpha coefficient:

>>>>

However, many researchers have also raised concerns that other factors, such as low power [@stanley2018what], lack of strong theoretical foundations [@eronen2021theory], and validity [@finkel2017replicability], which have not been given as much attention, are just as if not more responsible for the lack of successful replications found in psychology. Another factor which has gained more traction recently are measurement related issues' impact on replicability. In particular, studies have focused on the effects of issues such as measurement error and questionable measurement practices on replicability [@stanley2014expectations; @shaw2020measurement; @flake2017construct; @flake2020measurement].

Measurement in psychological science is defined in large part by one overarching issue: the psychological constructs of interest, such as affective state and intelligence, cannot be measured directly. As a result, psychologists face two primary challenges in the use of measurement: First of all, the measure has to assess the construct it intends to measure, even though it can only do so indirectly. Secondly, because the measurement is indirect, it also comes with some degree of error surrounding its assessment of the construct. The first issue relates to the concept of validity, and specifically construct validity. Validity refers to the overall extent to which a measure measures what it is supposed to [@borsboom2004concept], while construct validity specifically refers to the substantial relation between the item scores on a psychological measure and the psychological construct it intends to measure. In order for indirect assessment of psychological constructs to be a viable approach, the measure needs to have construct validity [@cook2002experimental]. The second issue relates to the concept of measurement error and reliability. Measurement error indicates the amount of variation in item scores that is the result of the used measures inaccuracies, and not due to differences in the underlying psychological construct of interest.

@stanley2014expectations demonstrated, using a simulation study, the impact measurement error has on attempts to verify or falsify findings. Scalar item data was generated based on levels of sampling error and score-reliability, as the inverse of measurement error, that mimicked what is standard in psychological research, to ensure that the resulting degree of error was representative. The results indicated that measurement error caused observed effects found in replication research to vary heavily.

Even when ignoring reliability, a measurement's content and implementation still need to validly capture what it intends to measure. Questionable Measurement Practices (QMPs) are practices that decrease the information that is necessary to evaluate a measurement's validity, and have been coined as a conjugate term to QRPs. They range from lack of transparency and unclear motivation in choice of measure, to poor justification for modifications of measure and procedure of any sourced measures [@flake2020measurement]. When this information is missing, it becomes difficult to establish that original and replication are measuring the same construct(s), which has detrimental consequences for direct replication attempts.

This study aims to investigate the influence of both measurement error and QMPs on replicability, using data and reports from the large scale Many Labs replication projects. One goal is to expand the research by [@stanley2014expectations] with a practical example. Whereas they obtained their findings using a simulation study, this study investigated the scope of their findings in practice. QMPs in the context of replication research were already investigated by [@flake2022construct]. However, the investigations remained mostly descriptive. This study additionally aims to expand upon the findings of [@flake2022construct] through the use of a new set of replication data, and by exploratively investigating the relation between QMP and replicability.

@@

As a first step the state of measurement error in original and replication research in psychology is investigated, to assess the scope of @stanley2014expectations's findings in practice:

@@

Since direct replications intend to investigate effects in nearly identical scenarios with nearly identical measures as the original study, it is expected that measurement errors are as present in the replication research looked at in this study as in the accompanying original psychological research.

@@

While reliability estimates are generally considered a measure specific feature, this is false. They are context dependent, and as a result the estimates of an effect can differ across contexts [@cho2015cronbach; @pauly2018resampling]. With large enough differences across contexts, the effect estimates between different replication attempts could deviate from each other beyond direct comparison. To investigate this potential problem, the variation in score reliability is assessed for each measure when used across a set of replications of the same effect in contexts.

@@

Even though reliability estimates are context dependent, sufficient protocol structure can counteract the variance in reliability estimates. An example of the standardizing impact a structured protocol can have on reducing variability within an effect can be found in investigations into the closely related issue of heterogeneity [@patacchini2007unobserved]. Heterogeneity refers to the true variation in the true effect size due to minor but key differences in context, environment, and procedure. Heterogeneity is yet another proposed explanation for failed replications. This concern even prompted a Many Labs centered around the testing of heterogeneity in replications [@klein2018many]. However analyses from Many Labs 2, and @olsson2020heterogeneity showed little empirical evidence for widespread heterogeneity in effects among replications. These findings demonstrate that it is possible to reduce variability as the result of context using structured protocols, as was done in the Many Labs projects this study analyzed.

@@

This study investigated whether there is something in the measures used for replicated findings that sets them apart from those used for non-replicated findings. One of the elements this study looked at is the reliability of replicated studies compared to the non-replicated studies, thus extending the research by @stanley2014expectations on the relationship between reliability and replicability with data from real life replication projects.

@@

## Questionable Measurement Practices
A measure not only needs to be reliable, it should also in its design and implementation adequately capture what it intends to measure [@flake2020measurement]. Any scientific report should therefore clearly motivate the use of measure and procedure. Without clear reporting on these aspects, the validity of measurement will remain uncertain. Therefore, the other tests of this paper focused on the reporting aspects of measurement, assessed through QMPs.

This study sought first of all to conceptually replicate some of the findings of @flake2022construct about QMP reporting in the RPP within the Many Labs replication projects.

@@

QMPs may obscure relevant information needed to evaluate the use of measurement in a study. If the replication used the measure differently from the original, the replication may no longer be a direct replication. As a result, there is additional deviation in the estimate of the effect from the original, due to differences in measurement. Establishing a link between QMPs and non-replicability should confirm suspicions of their detrimental effects on replications [@flake2017construct; @flake2020measurement; @flake2022construct].

@@

The total number of identified psychological findings for which replication was attempted across the four included Many Labs projects amounts to a total of `r sum(table(coded_data_replications$many_labs_version, coded_data_replications$appearance)[,1])`. Each finding was tested across several labs, and was related to a finding from an original study, the combination of all these studies and their associated information formed a replication set. For each research finding, any primary measures assessing a unique variable were taken to form the key unit of analysis. Here primary measures refers to measures assessing variables included in the primary test of the replication. This was done to ensure that the analyses could link directly to the replicability of a study. Acquiescence bias checks, manipulation checks, measures used for pilot testing, and measures added for exploratory analyses in replication studies were not included. The result was a total sample size of `r nrow(coded_data_replications)` measures used in both original and replication research [^1]. Table BELOW shows further descriptive information about the data for each Many Labs Project.

[^1]: Initially the original articles were coded to have 3 more measures than the replication protocols. However, these measures were all related to the moral foundations questionnaire, and could be altered from representing five different moral foundations to the two overarching categories of individualizing and binding foundations found described in the replication protocol without much issue or loss of information.

```{r ManyLabsDescriptivesTable, warning = FALSE}
# construct the Many Labs descriptives table to be printed
many_labs_descriptives_table <- data.frame("Many Labs Version" = c("1", "2", "3", "5", "Total"),
                                      "N ML Projects" = c(table(coded_data_replications$many_labs_version, coded_data_replications$appearance)[,1], sum(table(coded_data_replications$many_labs_version, coded_data_replications$appearance)[,1])),
                                      "N Primary Measures" = c(table(coded_data_replications$many_labs_version), nrow(coded_data_replications)), 
                                      "Replication Total N" = c(apa_num(mean(coded_data_replications$N[coded_data_replications$many_labs_version == "1"], na.rm = TRUE), digits = 0),
apa_num(mean(coded_data_replications$N[coded_data_replications$many_labs_version == "2"], na.rm = TRUE), digits = 0),
apa_num(mean(coded_data_replications$N[coded_data_replications$many_labs_version == "3"], na.rm = TRUE), digits = 0),
apa_num(mean(coded_data_replications$N[coded_data_replications$many_labs_version == "5"], na.rm = TRUE), digits = 0), apa_num(mean(coded_data_replications$N, na.rm = TRUE), digits = 0)), 
"Replication Total IQR" = c(apa_num(IQR(coded_data_replications$N[coded_data_replications$many_labs_version == "1"], na.rm = TRUE), digits = 0),
apa_num(IQR(coded_data_replications$N[coded_data_replications$many_labs_version == "2"], na.rm = TRUE), digits = 0),
apa_num(IQR(coded_data_replications$N[coded_data_replications$many_labs_version == "3"], na.rm = TRUE), digits = 0),
apa_num(IQR(coded_data_replications$N[coded_data_replications$many_labs_version == "5"], na.rm = TRUE), digits = 0), apa_num(IQR(coded_data_replications$N, na.rm = TRUE), digits = 0)),
"Original Total N" = c(apa_num(mean(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "1"], na.rm = TRUE), digits = 0),
apa_num(mean(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "2"], na.rm = TRUE), digits = 0),
apa_num(mean(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "3"], na.rm = TRUE), digits = 0),
apa_num(mean(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "5"], na.rm = TRUE), digits = 0), apa_num(mean(coded_data_original_shortened$N, na.rm = TRUE), digits = 0)),
"Original Total IQR" = c(apa_num(IQR(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "1"], na.rm = TRUE), digits = 0),
apa_num(IQR(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "2"], na.rm = TRUE), digits = 0),
apa_num(IQR(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "3"], na.rm = TRUE), digits = 0),
apa_num(IQR(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "5"], na.rm = TRUE), digits = 0), apa_num(IQR(coded_data_original_shortened$N, na.rm = TRUE), digits = 0)))

# Changing column names to be less computer speak-y looking
colnames(many_labs_descriptives_table) <- c("Many Labs Version", "N ML Projects", "N Primary Measures",
                                            "Replication Total N", "Replication Total IQR", "Original Total N", 
                                            "Original Total IQR")

# print the table in apa formatting
apa_table(
  many_labs_descriptives_table, align = c("l", "r", "r", "r", "r", "r", "r")
  , caption = "Descriptive information of number of included projects measures, and their sample size, across many labs projects for both original articles and replication protocols"
  , escape = FALSE, placement = "htp", midrules = 4)

@@

The data on the preregistered replication protocols, and replication datasets from Many Labs 1, 2, 3, & 5 were all retrieved from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>. Both the replication protocols and replication datasets were scanned through to ensure that the planned analyses were feasible. However, no coding or analysis of either of them had taken place before the analyses were preregistered. Further details on the search strategy can be found in the ??? supplementary materials.

@@

The replication datasets refer to the data of each of the replication attempts for each of the original psychological effects undertaken as part of a Many Labs study. These publicly available datasets of the replication attempt were accessed through their OSF page and loaded into Rstudio [@R-Rstudio]. When available, codebooks, analysis scripts and study materials were used to identify the specific data for each measure. The variables associated with each relevant measure were extracted into their own dataframe containing the data from all studies in one replication set. These dataframes together formed the dataset used for the analyses.

In order to be considered relevant for the analysis, the measure had to consist of multiple scalar items, as single item measures were not usable for the planned analyses on score reliability [@wanous1996estimating], following up on simulation study of @stanley2014expectations. If cleaned data was available this was chosen over raw data, to ensure that variables were coded as intended (e.g. no reverse-coded items). Pilot data were omitted from the analyses entirely. These criterion resulted in suitable measure data from `r apa_num(length(unique(data_h3_multiple$g)), numerals = FALSE)` replication sets spread across on average `r apa_num(mean(table(data_h3_multiple$g)), digits = 0)` lab locations for the analyses of hypotheses 2 & 3.

@@

The relevant OSF page of each replication set was searched through for a file which contained protocol in its name. If available, a version of the protocol labelled as revised, post-review, peer-review, or endorsed was selected. In case there was doubt about which was most appropriate, the latest uploaded relevant protocol was selected. Only regular protocols were taken, meaning those not labelled as data collection, analysis protocol or anything similar[^2].

[^2]: The steps taken to access the replication protocol data from Many Labs 5 were not preregistered, and only became clear upon further investigation of the accessible information. The specific names and locations of the files that were used as the datasets can be found under the supplementary materials of the OSF page of this article <https://osf.io/gft46/%7D>.

@@

The original articles were identified using the citations in each replication protocol. Then through searches via Web of Science, Google Scholar, and PsychInfo (in that order), the articles were retrieved[^3].

[^3]: An issue was encountered while trying to access @hyman1950current. However, after contacting the first author of @klein2014investigating a suitable version of the article was obtained for use in the analyses.

@@

@@

In order to answer questions regarding reported reliability, the reported reliability coefficient was extracted from both the replication protocols and the original articles. The reported reliability coefficient is the score reliability reported per measure in the replication protocol or original article. Both the type (Cronbach's alpha, retest, interrater, etc.) and the value itself were extracted.

@@

Cronbach's alpha was calculated as the main score reliability index used in the analyses, as remains the most commonly used indicator of the reliability of a measure. Cronbach's alpha was calculated using the alpha function from the psych R package [@R-psych]. Default arguments were used for the function.

@@

The tests for hypotheses 4, 5, & 6 were all based on the QMPs coded across both original articles and replication protocols. QMPs were all coded to be either true, false, or not applicable if not relevant for that particular measure (e.g. reporting results from a factor analysis in case a single item measure was used). Questions related to modification had 'no modification' as an additional answer option, in case the specific aspect of the measure was explicitly not modified. Each coded QMP belonged to one of five QMP type categories that were derived from the classification in @flake2020measurement. An overview of the QMP categories of the coding variables can be seen in Table \@ref(tab:QMPCodingInfoTable).

@@

Eleven out of twenty of the QMP variables used to calculate the QMP ratio have an equivalent in the coding key of @flake2022construct. The remaining nine were either altered from the coding key to better fit the QMP counting operationalization, all newly created or modified items were based on the definitions of the QMP categories and their criteria as specified in @flake2020measurement. Beside these quantitative variables, a total of four qualitative variables were also included to provide more detailed information on some aspects of the measure and its reporting. Details on the items used, their origin, changes, and justifications can be found in supplementary materials ???.

For the analyses of these variables both the total QMP ratios and ratios per QMP type category were used. This ratio was based on the number of coded trues divided by the total number of applicable QMPs. QMPs were considered applicable if not coded as not applicable or no modification. These ratios were preferred over counts, since non applicable items could thus be accounted for. Formula \@ref(eq:QMPRatioType) shows the formula that was used to calculate the QMP ratio for a particular QMP type j, where $True_{ij}$ is 1 if $item_{ij}$ was coded as True and 0 otherwise, and $False_{ij}$ is 1 if $item_{ij}$ was coded as False and 0 otherwise, $j \subset \{ definition, operationalisation, selection/creation, quanitification, modification \}$, and $i = 1,..., n_{j-items}$.

```{=tex}
\begin{equation}
QMP_ratio_{j} = \frac{\sum_{n=1}^i True_{ij}}{\sum_{n=1}^i True_{ij} + False_{ij}} (\#eq:QMPRatioType)
\end{equation}
```

For the total QMP ratio:

```{=tex}
\begin{equation}
QMP_ratio = \frac{\sum_{n=1}^j \sum_{n=1}^i True_{ij}}{\sum_{n=1}^j \sum_{n=1}^i True_{ij} + False_{ij}} (\#eq:QMPRatioTotal)
\end{equation}
```

After the data was initially coded according to the preregistered coding protocol, it was determined, based on discussion with the supervisor, that some of the initial ratings were possibly to stringent. As a result, some of the items in the protocol were reformulated, so that the conclusions from the resulting analyses were based on a more lenient judgement of QMPs. The revision of the coding protocol happened after all the data were coded using the initial protocol. As a result the coded data using the initial protocol, and the coded data using the revised protocol are both available on this article's OSF (<https://osf.io/9r8yt/>) and github (<https://github.com/CasGoos/measurement_and_replication.git>) pages. The analyses, tables and figures presented in this article are all based on the revised coding protocol, the equivalent results based on QMPs obtained with the initial protocol can be found in Appendix D.

@@

Every hypothesis test in this study used an alpha significance cutoff of .05. No correction for multiple testing was applied, to ensure that the rate of false negatives remained low, the increase in false positive rate was accepted as they deemed less harmful to the exploratory aims of this study.

@@

The pre-registered test for hypothesis 1, a t-test of the reported Cronbach's alpha coefficient values between original and replication, could not be conducted, since not enough score reliabilities were reported to conduct the test and expect sensible results. Instead, the total number of reported reliability coefficients were compared between the replication protocols and the original articles. This comparison was tested via a chi-square test using the base R stats package [@R-base].

@@

While reported reliabilities were rare, reliabilities could still be calculated from `r apa_num(length(unique(data_h3_multiple$g)), numerals = FALSE)` replication datasets. On top of that, reliabilities could be calculated for each individual lab per replication set so that the variance of the coefficients of a single measure could be assessed. In order to separate between and within variance in reliability, a multilevel random intercept model was specified with replication set as the grouping variable and the Cronbach's alpha value of a replication as dependent using the lmer function from the lme4 package [@R-lme4]. The formulas for this model, where $alpha_{ij}$ represents the calculated Cronbach's alpha coefficient of a single study at one lab location with $i = 1,..., n_{locations}$ and $j = 1,...,n_{replicationsets}$ look as follows:

@@

@@

```{r ICCCalculations, include = FALSE}
# Variances
within_group_variance_alpha <- attr(VarCorr(H2_test_result_alpha), "sc")^2
between_group_variance_alpha <- attr(VarCorr(H2_test_result_alpha)$g, "stddev")^2

# ICC
ICC_alpha <- between_group_variance_alpha / (within_group_variance_alpha + between_group_variance_alpha)

@@

After the pre-registration was registered, and data had been collected and analysed, it came to the author's attention that it is possible to conduct meta-analyses on reliability coefficients, commonly referred to as Reliability Generalization Meta-Analyses [@botella2012ManagingHeterogeneityVariance; @lopez-ibanez2024ReliabilityGeneralizationMetaanalysis]. Using meta-analysis, it is possible to quantify within the model the degree of true variation in the metric of interest across samples [@cooper2019handbook]. Subsequently, the true variation in the metric, or heterogeneity, can be tested to constitute a significant part of the total variation in the observed estimates of the metric or not.

Because heterogeneity estimates line up well as a test for hypothesis 2, a random-effects meta-analysis was conducted on the calculated Cronbach's alpha for each measure for which replication datasets were available and usable. The rma function from metafor package [@R-metafor] was used to run the meta-analysis. No correction for bias or weighting of the effects has been implemented, to reduce model complexity, and because the data came from Many Labs replication projects and not typical literature.

A meta-analysis requires an estimate of the standard error in order to be conducted. For Cronbach's alpha, formulas 2 & 3 from @duhachek2004AlphaStandardError was used to calculate alpha's standard error. Heterogeneity was estimated using the tau value, meaning the standard deviation of the distribution of true Cronbach's alpha coefficients for that measure, and tested using the Cochran's Q test for each measure.
